Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-20 Scripts/Initial_Analysis.Rmd
Updates to code

---
title: Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for
  Policy Response Under Climate Change
author: "Juliano Palacios Abrantes"
date: "09/03/2020"
output:
  word_document: default
  html_document: default
subtitle: Initital analysis
editor_options: 
  chunk_output_type: console
---

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt" # for estimating distances between points
)

@@

ggtheme_map <- function(base_size = 9, Region = "NA") {

@@

@@

```{r dbem_import, eval = F, echo = T}

@@

## Determine Coords centroids and Neighbouring ids

```{r, get_eez_centroids, eval = F}

@@

write_csv(coords,
          "eez_centroids.csv")

@@

#  set ids 
df1 <- Neighbours_spp
df2 <- Neighbours_spp
colnames(df2) <- c("neighbour_id", "eez_neighbour", "eez_name")

df_full <- bind_rows(df1, df2) %>% 
  group_by(eez_neighbour,eez_name) %>% 
  summarise(neighbour_id = min(neighbour_id))

# write_csv(df_full, "Neighbours_eez_id.csv")

@@

#### Fun `EstPropChange`

@@

EstPropChange <- function(taxon_key,
                          year,
                          data_type,
                          ensamble_list, # expects a list of ensambles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensambles
  spp_dist <- bind_rows(
    lapply(
      ensamble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

  # head(spp_dist)

  # Result 1. Number of Countries that share the species

  suppressWarnings(
    trans_EEZ <- Transboundary_spp %>% 
      filter(taxon_key %in% spp_dist$taxon_key) %>% 
      left_join(Neighbours,
                by = c("eez_name","eez_neighbour")
      )
  )

  # List of indexes per EEZ
  index_id <- trans_EEZ %>% 
    group_by(eez_name,index) %>% 
    summarise(n=n()) %>% 
    select(-n)

  # --------------- #
  # Warning messages:
  # 1: Column `eez_name` joining factor and character vector, coercing into character vector 
  # 2: Column `eez_neighbour` joining factor and character vector, coercing into character vector 
  # --------------- #

  #____________ Selecting only the transboundary nature of the species _________ #
  trans_spp <- spp_dist %>%
    filter(index %in% trans_EEZ$index) %>% 
    left_join(index_id,
              by = "index")

  #____________ ESTIMATING DISTRIBUTION INDEX (TRESHOLD 3)_________ #
  # The number of species' cells present within each country's EEZ

  #Step 1.  Get EEZ id and Neighbour
  Neighbours_List <- Neighbours %>% 
    group_by(eez_name,eez_neighbour) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    select(-n) %>% 
    semi_join(trans_EEZ,
              by = c("eez_name","eez_neighbour")
    )

  # Step 2. Determines the amount of grids present in each country
  spp_grid <- trans_spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensamble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Step 3. Sum total grids per Neighbours

  # Split dataframes to merge latter
  Territory_T <- spp_grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      year,
      ensamble
    )

  Neighbour_T <- spp_grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      Name=eez_neighbour,
      eez_name,
      year,
      ensamble
    )

  per_change_d <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensamble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # select(taxon_key,year,ensamble_list,eez_name,eez_neighbour,area_index) %>% 
    mutate(
      time_step = ifelse(year < 2000,"historical",
                         ifelse(year >= 2045 & year <= 2064, "mid",
                                ifelse(year >= 2080, "n_end","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensamble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # Ensamble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("temporal_mean"),
                 c(ensamble_mean=mean,
                   ensamble_sd=sd),
                 na.rm=T
    )

@@

  if(nrow(per_change_d) > 0){

@@

  write_csv(per_change_d,
            path_name)

  return(print(paste("analysis done",taxon_key)))

@@

  # Or return a df
  # return(per_change_d)
}

@@

#### Proportion routine

@@

#### Fun `GetCentroids`

@@

```{r GetCentroids, eval = F, echo = T}

GetCentroids <- function(taxon_key,year, data_type = "Catch", ensamble, path, Neighbours, eez_centroid){

@@

  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = "Catch",
    ensamble = ensamble,
    path = path
  )

@@

    # Run function
    Centroids_Data <- bind_rows(
      lapply(Ids,CentroidsFx)
    )

    Centroids_Data <- tibble()

@@

@@

#### Fun `TransIndex`

TransIndex <- function(Centroids,Ids){

@@

  # Historical mean and sd of distance
  historical <- Centroids_id %>%
    filter(year <= 2000) %>% 
    ungroup() %>%
    group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
    summarise_at(vars("distance"),
                 c(hd_temp_mean=mean,
                   hd_temp_sd=sd)
    )

  # Future results
  future <- Centroids_id %>% 
    filter(year > 2000)

@@

  Unique_EEZs <- unique(Trans_index$eez_name)

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    group_by(taxon_key,ensamble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

@@

@@

@@

# test <- bind_rows(
#   lapply(ensamble_list,
#          GetCentroids,
#          taxon_key = 600245,
#          year = year,
#          data_type = "Catch",
#          path = path,
#          Neighbours = Neighbours,
#          eez_centroid = eez_centroid)
# )
# 
# 
#   TransIndex(test,819)
#   
#   bind_rows(
#   lapply(Ids,
#          TransIndex,
#          Centroid = test)
#   )

@@

#### Fun `GetTransIndex`

@@

GetTransIndex <- function(taxon_key,
                            year,
                            data_type = "Catch",
                            path,
                            ensamble_list,
                            Neighbours,
                            eez_centroid){

    # First step
    # Call Get centroids fucntion for centroids data per ensamble
    Step_one <- bind_rows(
      lapply(ensamble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = "Catch",
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

    Ids <- unique(Step_one$neighbour_id)

    # Second Step
    # Get the transboudary index based on all centroids
    Step_two <- bind_rows(
      lapply(Ids,
             TransIndex,
             Centroid = Step_one)
    )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensamble_list = ensamble_list,
  #   year = year,
  #   data_type = "Catch",
  #   path = path,
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )
  # 
  # 
  # spp_list <- c(600004, 600245)
  # 
  #  test <- bind_rows(
  #   lapply(spp_list,
  #          GetTransIndex,
  #          year = year,
  #          data_type = "Catch",
  #          path = path,
  #          Neighbours = Neighbours,
  #          eez_centroid = eez_centroid,
  #          ensamble_list = ensamble_list
  #   )
  # )
  #

@@

#### Emerging Control Panel

@@

# Data needed for estimating Proportion change

# SAU relations between INDEX and Country's EEZs
EEZIDs_List <- read_excel(paste(data_path,"Spatial/V_Lam/Updated_EEZList_17June2016.xlsx",sep="")) %>% 
  clean_names()
EEZ_CellID <- read_excel(paste(data_path,"Spatial/V_Lam/EEZ_CellID.xlsx",sep="")) %>% 
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

year_df <- tibble(year =  c(seq(1951,2000,1), seq(2001,2099,1)),
                  time_period = c(rep("historic", 50), rep("future", 99))
                  )

data_type <- "catch"
# ensamble_list <- seq(102,103,1)
ensamble_list <- seq(102,111,1)

world_grid <- tibble(index = seq(1,259200,1))
path = DBEM_path

eez_centroid <- read.csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""), header=TRUE)

Neighbours <- read.csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names()

spp_list <- unique(Transboundary_spp$taxon_key)[1:2]

@@

#### Emerging Routine

@@

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year,
               data_type = "Catch",
               ensamble_list = ensamble_list,
               path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

write_csv(Test,
          "~/Desktop/Test.csv")

@@

  if(links == "y"){
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

The next step is to summarize all species per eez

@@

# Get taxon list
taxon_list <- list.files(paste(result_path,"/Proportion/",sep=""))

# clean names for function
taxon_list <- gsub(".*_","",taxon_list) 
taxon_list <- gsub("\\..*","",taxon_list)

# Run results
results <- PropChange(taxon_list, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

@@

# Call world map from natural earth
world_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf"))

coords <- read.csv(coords)

@@

World_sf %>% 
  left_join(results,
            by = "eez_name") %>% 
  filter(variable %in% c("mean_spp")#,
         # eez_name %in% c("Peru","Chile","Ecuador","Argentina")
         ) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = per_mid
    )
  ) + 
  geom_sf(data=country10_sf) +
  scale_fill_gradient2("Average Change in\nStock-Share Ratio (%)\nBy Mid Century") +
  ggtheme_map() +
  ggsave("figure_one.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

# Figure made thanks to Juanito!
# http://jsmayorga.com/post/mapping-the-global-network-of-transnational-fisheries/

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(coords,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(coords,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>% 
  filter(per_mid > 0,
         variable == "mean_spp"#,
         # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

x <- ggplot() +
  geom_sf(data = world_map, size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = Data,
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "black",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = paths,
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc")),
            show.legend = NA) +
  # geom_sf_text(data =World_eez_sf, aes(label =eez_name),
  #              size = 2) +
  # geom_text_repel(data = paths,
  #                  aes(
  #                    x = X,
  #                    y = Y,
  #                    label =source),
  #                  force = 1
  # )+
  ggtheme_map() +
  scale_colour_gradientn("Gain of Stock-Share Ratio (%)",
                         colours = wesanderson::wes_palette("Zissou1", 100, type = "continuous"),
                         limits = c(0,25),
                         breaks = seq(0,25,5)
  )+ 
  ggsave("figure_connections.png",
         width = 10,
         height = 6,
         units = "in"
  )

>>>>

---
title: Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for
  Policy Response Under Climate Change
author: "Juliano Palacios Abrantes"
date: "09/03/2020"
output:
  word_document: 
    keep_md: yes
  html_document: default
subtitle: Initital analysis
editor_options: 
  chunk_output_type: console
---

```{r setup, eval = T, echo = F, warning = F, message = F, results = 'hide'}

@@

#### Project's Library
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt" # for estimating distances between points
)

@@

# standarize maps
ggtheme_map <- function(base_size = 9, Region = "NA") {

@@

See methods section of the paper (e.g. Manusript.Rmd)

## Global functions

Here we just run functions that will be used multiple times douring the analysis

@@

```{r dbem_import, eval = T, echo = T}

@@

## Creating Data

Here we re-arrange existing data for the analysis. We have three steps:

1- Set the SAU relations between index and EEZs and include lat long data for each index

2.- Deteremine the centroid of each EEZ and asigned an id to each neighbouring interaction (e.g. Chile and Peru or Canada West Coast and US West Coast)

3.- Set Neigbouring IDs based on the interactions between neighbouring EEZs for all of those sharing transboundary species

```{r pre_data_creation, eval = F, echo = F}

## ---------------##
#### 1. SAU relations between INDEX and Country's EEZs
## ---------------##

EEZIDs_List <- read_excel(paste(data_path,"Spatial/V_Lam/Updated_EEZList_17June2016.xlsx",sep="")) %>% 
  clean_names()
EEZ_CellID <- read_excel(paste(data_path,"Spatial/V_Lam/EEZ_CellID.xlsx",sep="")) %>% 
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

write_csv(index_code,
          "sau_index_code.csv")

## ---------------##
#### 2. entroids 
## ---------------##

@@

# Save dataframe so we don't need to run this ewvery time
# write_csv(coords,
#           "eez_centroids.csv")

## ---------------##
#### 3. Set Neigbouring IDs
## ---------------##

# Read transboundary species database from Palacios-Abrantes et al 2020 (FishForVisa)
Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names()

@@

# Split dataframes to merge neighbouring ids
df1 <- Neighbours_spp
df2 <- Neighbours_spp
colnames(df2) <- c("neighbour_id", "eez_neighbour", "eez_name")

# Merge neighbouring ids
df_full <- bind_rows(df1, df2) %>% 
  group_by(eez_neighbour,eez_name) %>% 
  summarise(neighbour_id = min(neighbour_id))

# Save dataframe so we don't need to run this every time
# write_csv(df_full, 
#           "Neighbours_eez_id.csv")

@@

This part of the analysis estimates the Stock Share Ratio and its change under cliamte change under two time frames; early (2030) and mid (2050). Note that 2020 is the average of 2021 to 2040 and mid is the average of 2041 to 2060.

### Fun `EstPropChange`

@@

EstPropChange <- function(taxon_key,
                          year,
                          hist_y,
                          data_type = "Catch",
                          ensamble_list, # expects a list of ensambles to averrage by
                          path,
                          neighbours){

  # Loads species data for all ensambles
  Spp_Dist <- bind_rows(
    lapply(
      ensamble_list,
      dbem_import,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
      path = path
    )
  )

  # Filter Species distribution to that of the neighbouring EEZs
  # ------------ #
  # Warning message:
  # Column `eez_name` joining factor and character vector, coercing into character vector 
# ------------ #

  suppressWarnings(
    Trans_EEZ <- Transboundary_spp %>% 
      filter(taxon_key %in% Spp_Dist$taxon_key) %>% 
      left_join(index_code,
                by = c("eez_name")
      )
    )

  # Get neighbouring id
  Neighbours_List <- Neighbours %>% 
    semi_join(Trans_EEZ,
              by = c("eez_name","eez_neighbour")
    )

  # Selecting only the transboundary nature of the species
  Trans_Spp <- Spp_Dist %>%
    filter(index %in% Trans_EEZ$index) %>% 
    left_join(index_code,
              by = "index") %>% 
    filter(eez_name %in% Neighbours_List$eez_name)

  # -------------------- #
  # Estimate area index
  # The number of species' cells present within each country's EEZ
  # -------------------- #

  #Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensamble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name")

  # Split dataframes to merge latter
  Territory_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      Name=eez_name,
      n_spp_eez,
      year,
      ensamble
    )

  Neighbour_T <- Spp_Grid %>% 
    ungroup() %>% 
    select(
      taxon_key,
      n_spp_eez,
      Name=eez_neighbour,
      eez_name,
      year,
      ensamble
    )

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensamble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensamble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # Ensamble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("temporal_mean"),
                 c(ensamble_mean=mean,
                   ensamble_sd=sd),
                 na.rm=T
    )

@@

  if(nrow(Per_Ghange_D) > 0){

@@

  write_csv(Per_Ghange_D,
            path_name)

  return(print(paste("analysis done",taxon_key)))
  # return(Per_Ghange_D)

@@

  # Or return a df
  return(Per_Ghange_D)
}

# EstPropChange(taxon_key = 600004,
#               year = year_df,
#               hist_y = 2000,
#               data_type = "Catch",
#               ensamble_list = ensamble_list,
#               path = path,
#               neighbours = neighbours)

@@

### Proportion Control Panel

## ----------------- ##
# Data needed for estimating year of emergence
## ----------------- ##

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- read_csv(paste(data_path,"Spatial/sau_index_code.csv",sep=""))

# Neighbour list and their respective id (see chunk 3)
Neighbours <- read_csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- read_csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names() %>% 
  select(-x1)

## ----------------- ##
# Global variables
## ----------------- ##

# Year timeframe
year_df <- tibble(year =  c(seq(1951,2000,1), seq(2001,2099,1)),
                  time_period = c(rep("historic", 50), rep("future", 99))
                  )

# Data path
path = DBEM_path

# List of ensamble members
ensamble_list <- seq(102,103,1) # for testing
# ensamble_list <- seq(102,111,1)

#  List os species
spp_list <- unique(Transboundary_spp$taxon_key)[1:2]

### Proportion routine

@@

This rutine estimates the time (e.g. year) in which the changes in stock share ratio is more likely to happen based on historical variations (e.g. model noise) and future trends (e.g signal). This result uses teh average of the 10 ensamble members

### Fun `GetCentroids`

@@

```{r GetCentroids, eval = T, echo = F}

GetCentroids <- function(taxon_key,
                         year, 
                         data_type = "Catch",
                         ensamble, 
                         path,
                         Neighbours,
                         eez_centroid){

@@

  Spp_Dist <- dbem_import(
    taxon_key = taxon_key,
    year = year,
    data_type = data_type,
    ensamble = ensamble,
    path = path
  )

@@

    # Run sub-function
    Centroids_Data <- bind_rows(
      lapply(Ids,CentroidsFx)
    )

  }else{
    # In case there's no data
    Centroids_Data <- tibble()

@@

GetCentroids(taxon_key = 600004,
             year = year_df,
             # data_type = data,
             ensamble = 102,
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid
             )

@@

### Fun `TransIndex`

This functions takes on `GetCentroids` function and estimates the TransIndex (*TI*) for each pair of neighbouring countries. Presents a 10 years average of the results

$$TI =(\frac{D_{A,y}}{sd(D_{A,h})} - \frac{D_{B,y}}{sd(D_{B,h)}})^2$$

The year of emergece is defined as the first year where the trend is larger than the 95% CI of the historic variation.

```{r TransIndex, eval = T, echo = T}

TransIndex <- function(Centroids, # Expecting the results from the GetCentroids function
                       Ids, # A numeric value representing a neighbouring interaction
                       Hist_y = 2000){ # The LAST year of Historical data

@@

  # Historical mean and sd of distance
  historical <- Centroids_id %>%
    filter(year <= Hist_y) %>% 
    ungroup() %>%
    group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
    summarise_at(vars("distance"),
                 c(hd_temp_mean=mean,
                   hd_temp_sd=sd)
    )

  # Future results
  future <- Centroids_id %>% 
    filter(year > Hist_y)

@@

  # Get unique eezs
  Unique_EEZs <- unique(Trans_index$eez_name)

  Partial <- Trans_index %>% 
    mutate(
      names = ifelse(eez_name ==Unique_EEZs[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
    ) %>%
    select(-eez_name,-variable) %>%
    spread(names,value) %>% 
    # mutate index
    mutate(
      trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
    ) %>% 
    # Ten years average of results
    group_by(taxon_key,ensamble,neighbour_id) %>% 
    mutate(RMean = rollmean(x = trans_index, 
                            10, 
                            align = "right", 
                            fill = trans_index)
    ) %>% 
    filter(year > 1960) %>% 
    select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

@@

  # Estimate noice from ensamble members
  historic_sd <- mean_sd_index %>% 
    filter(year < Hist_y) %>% 
    group_by(taxon_key) %>% 
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd)
    )

@@

  # Identifies the year of emergence
  Final_Result <- mean_sd_index %>%
    filter(year > Hist_y,
           trend > (historic_sd$hist_mean+historic_sd$noise) |
             trend < (historic_sd$hist_mean-historic_sd$noise)
    ) %>%
    group_by(taxon_key,neighbour_id) %>%
    summarise(emerging_yr= min(year)) %>%
    left_join(EEZ_ids) %>%
    ungroup() %>%
    select(taxon_key,eez_name,eez_neighbour,emerging_yr)

@@

@@

### Fun `GetTransIndex`

This is the last function of the emerging year evaluation. It was made so we could run the analysis per each species. The function function simply runs the functions `GetCentroids` by ensabmble member and then `TransIndex` by pairing EEZ. Thus, with this function we run the whole set by species * paired EEZ * ten ensamble members.

@@

GetTransIndex <- function(taxon_key,
                            year,
                          Hist_y,
                            data_type = "Catch",
                            path,
                            ensamble_list,
                            Neighbours,
                            eez_centroid){

    # First step
    # Call Get centroids fucntion for centroids data per ensamble
    Step_one <- bind_rows(
      lapply(ensamble_list,
             GetCentroids,
             taxon_key = taxon_key,
             year = year,
             data_type = data_type,
             path = path,
             Neighbours = Neighbours,
             eez_centroid = eez_centroid)
    )

    # Set the different neighbouring pairs
    Ids <- unique(Step_one$neighbour_id)

    # Second Step
    # Get the transboudary index based on all centroids
    Step_two <- bind_rows(
      lapply(Ids,
             TransIndex,
             Hist_y = Hist_y,
             Centroid = Step_one)
    )

@@

  # GetTransIndex(
  #   taxon_key = 600004,
  #   ensamble_list = ensamble_list[1:2],
  #   year = year,
  #   Hist_y = 2000,
  #   data_type = "Abd",
  #   path = path,
  #   Neighbours = Neighbours,
  #   eez_centroid = eez_centroid
  # )

  # spp_list <- c(600004, 600245)
  # 
  #  test <- bind_rows(
  #   lapply(spp_list,
  #          GetTransIndex,
  #          year = year,
  #          data_type = "Catch",
  #          path = path,
  #          Neighbours = Neighbours,
  #          eez_centroid = eez_centroid,
  #          ensamble_list = ensamble_list
  #   )
  # )
  #

@@

### Emerging Control Panel

@@

## ----------------- ##
# Data needed for estimating year of emergence
## ----------------- ##

# SAU relations between INDEX and Country's EEZs (see chunk 3)
index_code <- read_csv(paste(data_path,"Spatial/sau_index_code.csv",sep=""))

# EEZ list and their centroid of distribution (see chunk 3)
eez_centroid <- read.csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""), header=TRUE)

# Neighbour list and their respective id (see chunk 3)
Neighbours <- read.csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

# Transboundary species and their sharing EEZs (see Palacios-Abrantes et al; FishForVisa)
Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% 
  clean_names()

## ----------------- ##
# Global variables
## ----------------- ##

# Year timeframe
year_df <- tibble(year =  seq(1951,2099,1))

# Last year of "historic" data
Historic_year = 2000

# Data path
path = DBEM_path

# List of ensamble members
ensamble_list <- seq(102,103,1) # for testing
# ensamble_list <- seq(102,111,1)

#  List os species
spp_list <- unique(Transboundary_spp$taxon_key)[1:2]

@@

### Emerging Routine

@@

suppressMessages(
  suppressWarnings(
    Emerging_result <- bind_rows(
      mclapply(spp_list[1],
               GetTransIndex,
               year = year_df,
               Hist_y = Historic_year,
               data_type = "Catch",
               ensamble_list = ensamble_list,
               path = path,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid
      )
    )
  )
)

@@

write_csv(Emerging_result,
          "~/Desktop/Test.csv")

@@

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

The next step is to summarize all species per eez so our results shows average change of all species within an EEZ towards a neighbour

@@

# Get taxon list
Taxon_List <- list.files(paste(result_path,"/Proportion/",sep=""))

# clean names for function
Taxon_List <- gsub(".*_","",Taxon_List) 
Taxon_List <- gsub("\\..*","",Taxon_List)

# Run results
Proportion_Results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

@@

# Call world map from natural earth
World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf"))

eez_centroid <- read_csv(paste(data_path,"Spatial/eez_centroids.csv", sep = ""))

@@

World_sf %>% 
  left_join(results,
            by = "eez_name") %>% 
  filter(variable %in% c("mean_spp")#,
         # eez_name %in% c("Peru","Chile","Ecuador","Argentina")
         ) %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = per_mid
    )
  ) + 
  geom_sf(data=country10_sf) +
  scale_fill_gradient2("Average Change in\nStock-Share Ratio (%)\nBy Mid Century") +
  ggtheme_map() +
  ggsave("per_mid.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

```{r fig_map_Juan, eval = F, echo =F}
# Figure made thanks to Juanito!
# http://jsmayorga.com/post/mapping-the-global-network-of-transnational-fisheries/

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

gc()# clean ram
x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,25),
    breaks = seq(0,25,5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connectionsc.png",
         width = 10,
         height = 6,
         units = "in"
  )
